\documentclass[xetex]{moderncv}
 
\usepackage{fontspec}
\usepackage{xunicode} 
\usepackage{xltxtra}  
\usepackage[english]{babel}

\defaultfontfeatures{Mapping=tex-text, Scale=MatchLowercase}

\moderncvtheme[blue]{classic}
\firstname{Artem}
\familyname{Onuchin}
\mobile{+7 (915) 361-86-01}
\email{onuchinart@gmail.com}
\homepage{www.linkedin.com/profile/view?id=183758089}

\begin{document}
\frenchspacing
\lefthyphenmin=3
\righthyphenmin=3
\clubpenalty=10000 
\widowpenalty=10000
\maketitle
{\Large I am open for remote work or relocating if visa is sponsored.}

\section{Employment}
\cventry{Apr 2013 -- working now}{Software engineer}{Yandex LLC}{Moscow}{}{
\href{http://market.yandex.ru}{Yandex.Market} is a leading Russian eCommerce web-service. \\
I am responsible for Market data infrastructure. The systems that I build and support ensure the sustainability of billing the most of Market money, improve the quality of clicks that we sell to our clients and help taking data-driven decisions. \\
 As part of my team I've participated in many projects about data-products such as AB-testing, Antifraud and CTR prediction. \\
 My role in Market team implied the following activities: \\
\begin{itemize}
\item Building from scratch new production-quality components.
\item Optimizing hadoop data-flow.
\item Debugging complicated  heisen bugs.
\item Moving all data to Hive.
\item Maintaining hadoop MapReduce and HDFS settings.
\end{itemize}
}
\cventry{Oct 2012 -- Apr 2013}{Senior software developer}{VideoInternational}{Moscow}{}{
Worked in team that was building RTB-system. I've built integration with several Data Suppliers.}
\cventry{Mar 2011 -- Oct 2012}{Software developer}{Openstat.ru}{Moscow}{}{
Worked in small company that provided services of web-analytics. \\
On this job I've implemented the number of various reports for our clients.\\
Also I've rewrote the system of scheduling Cascading tasks. It improved the average time of hourly workflow and improved the time that needed to normalize calculation lags.
}
\cventry{Mar 2010  -- Mar 2011}{Software developer}{ContextWeb}{Moscow (outsourcing)}{}{
Worked in ad-network company in Data team.}
\section{Skills set}
Java SE, Apache Hadoop, Unix scripting, Multithreading, Distributed Systems, Sql, Apache Hive, Python, R, Data Analysis, Algorithms

\pagebreak

\section{Education}
\cventry{2007 -- 2011}{Bachelor of Science} {Russian Social State University} {Moscow}{}{Computer science}

\section {Aditional education}

I like educating and I took a some MOOC's:  
\begin{itemize}
\item \href{https://www.dropbox.com/s/ey4kpuspil6ez54/Statement\%20of\%20Accomplishment.pdf}{Coursera, Machine Learning }
\item \href{https://www.dropbox.com/s/ot8hvdck28tyoj4/AlgoDA2.pdf}{Coursera,  Algorithms: Design and Analysis pt.2 }
\item \href{https://www.dropbox.com/s/ikqocsfb94sot51/in_memory_data_management_certificate_full_15656.pdf}{OpenHPI, In Memory Data Management }
\end{itemize}
and some courses in \href{http://shad.yandex.ru/?ncrnd=6964}{The School of Data Analysis}:
\begin{itemize}
\item \href{http://shad.yandex.ru/program/algorithms1.xml}{ Algorithms and data structures}
\item \href{http://shad.yandex.ru/program/algorithms3.xml}{ Algorithms for big data processing}
\item Applied analytical problems in information retrieval
\end{itemize} 
\section {Awards}
I have taken first place in Yandex Open Data Hackaton 2013.
\end{document}
